Order reduction and MILP models for real-time DNN robustness certification.

### 2025-11-13 CAV 2026/experiments.tex
results
RESULTS + SPREAD

>>>>

\subsection{Global Robustness Comparison vs Vhagar and ITNE}

To be able to compare with Vhagar, we have to use Vhagar benchmarks: 
perturbation they consider (here $L_\infty=0.05$) on their DNNs (here Conv1 for MNIST, FMNIST and CIFAR-10), for which the reduction rules of binary variables are implemented. We test with 1000s Time-Out, as well as one test with 14400s time out, showing that much longer time-out does not have a big impact on the result.

The spread is the average over all cases of the relative distance between the bound to the highest worst-case for that case.

\begin{table}[h!]
	\centering
	\begin{tabular}{||c||c|c|c|c|c||}\hline\hline
	Benchmark & model & Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ & $\%$ of spread $\downarrow$ \\\hline \hline
	MNIST   & Vhagar & 20.51 & 9.20 & 9.20 & 118 $\%$
    \\
	M-Conv1 & ITNE & 12.77 & 9.41 & 9.41 & 35 $\%$
	\\ 
    TO=1000s & "2v" & {\bf 11.59}  & 9.38 & 9.38 & {\bf 23 $\%$}
    \\\hline \hline

	FMNIST & Vhagar &  ? &  ? & ? & ?
    \\
	F-Conv1  & ITNE &  $27.57$ &  $22.12$ & $22.12$ & 23 $\%$
	\\ 
    TO=1000s & "2v" &  {\bf 23.67} &  $22.31$ &  $22.31$ & {\bf 6 $\%$}
    \\\hline

	FMNIST & Vhagar &  $37.01$ &  $22.06$ & $22.06$ & 67 $\%$
    \\
	F-Conv1  & ITNE &  $24.56$ &  $22.20$ & $22.20$ & 10 $\%$
	\\ 
    TO=14400s & "2v" &    {\bf 22.84} &  $22.53$ &  $22.53$ & {\bf 1 $\%$}
    \\\hline \hline

	CIFAR-10  & Vhagar & does & not & run & 
    \\
	C-Conv1  & ITNE &  & & &
	\\ 
    TO=1000s & "2v" &    & & &
    \\\hline \hline

     \end{tabular}
	\caption{Comparison with Vhagar for $L_\infty=0.05$ perturbation.}
    \label{table.classical}
\end{table}
